---
title: "Descriptive"
---

Load packages for exploratory data visualization, and prep data

```{r, message=FALSE, warning=FALSE}

library(DataExplorer)
library(GGally)
library(colorEvoHelpers)
library(dplyr)

wings <- read.csv("data/wings.csv")

wings$blackbrown <- wings$black
wings$brownyellow <- wings$brown
wings$sex <- wings$Sex
wings$wing_length <- wings$Length..outer..FW..mm.
wings$temperature <- wings$temp_indv
wings$flight_type <- wings$flight_type_rm_inter
wings$is_damselfly <- wings$Suborder == "Zygoptera"

```

What colors have come out of our clustering?

```{r}

row <- wings[1,]

plotRGB(c(row$col_1_r,row$col_1_g,row$col_1_b),max=1)
plotRGB(c(row$col_2_r,row$col_2_g,row$col_2_b),max=1)
plotRGB(c(row$col_3_r,row$col_3_g,row$col_3_b),max=1)
```

Visualize the distribution of the Odonate percher-flyer dichotomy (flight_type) and sex in the dataset

```{r}

plot_bar(select(wings, flight_type, sex))
```

1.  Many more perchers than flyers
2.  More males than females

Visualize distributions of continuous predictors and responses

```{r}

plot_density(select(wings,blackbrown,brownyellow,temp_indv,wing_length)) #temp_indv,lat,lon,mean_lightness))
```

Many zeroes in black-brown and brown-yellow, while wing length is close to a normal distribution

Visualize correlations between pertinent variables

```{r}

plot_correlation(select(wings,blackbrown,brownyellow,temp_indv,Length..inner..FW..mm.,flight_type, Sex))
```

What collections are specimens from?

```{r}

library(dplyr)
supp <- wings %>%
  select(Collection,Collection.Unique.ID) %>%
  distinct(Collection.Unique.ID, .keep_all = TRUE)

View(supp)

table(supp$Collection)

supp$Col <- supp$Collection

supp$Col[supp$Collection == "UA"] <- "Alabama Museum of Natural History"
supp$Col[supp$Collection == "MLM"] <- "Collection of Michael L. May"
supp$Col[supp$Collection == "RUN"] <- "Rutgers-University Newark (Now Housed at AMNH)"
supp$Col[supp$Collection == "WRK-WS"] <- "Collection of William Kuhn (Now Housed at AMNH)"

colnames(supp) <- c("collection_code","collection_unique_id", "collection_name")
```
