---
title: "Descriptive"
---

Load packages for exploratory data visualization

```{r, message=FALSE, warning=FALSE}

library(DataExplorer)
library(GGally)
library(colorEvoHelpers)
library(dplyr)

# prep isn't tested currently, so load in data already created for now
wings <- read.csv("data/wings.csv")
# wings_new <- read.csv("data/wings_new.csv")
```

What colors have come out of our clustering?

```{r}

row <- wings[1,]
# three are notably darker, and looking at images correspond to visibly pigmented areas
plotRGB(c(row$col_1_r,row$col_1_g,row$col_1_b),max=1)
plotRGB(c(row$col_2_r,row$col_2_g,row$col_2_b),max=1)
plotRGB(c(row$col_6_r,row$col_6_g,row$col_6_b),max=1)
# other 3 are different shades of white and tan, shades of unpigmented wings
plotRGB(c(row$col_3_r,row$col_3_g,row$col_3_b),max=1)
plotRGB(c(row$col_4_r,row$col_4_g,row$col_4_b),max=1)
plotRGB(c(row$col_5_r,row$col_5_g,row$col_5_b),max=1)
```

Visualize the distribution of the Odonate percher-flyer dichotomy (flight_type) and sex in the dataset

```{r}

plot_bar(select(wings, flight_type, Sex,Family))
```

1.  Many more perchers than flyers
2.  More males than females

Visualize distributions of continuous predictors and responses

```{r}

plot_density(select(wings,black,brown,yellow,temp_indv,Length..inner..FW..mm.)) #temp_indv,lat,lon,mean_lightness))
```

Visualize correlations between pertinent variables

```{r}

plot_correlation(select(wings,black,brown,yellow,temp_indv,Length..inner..FW..mm.,flight_type, Sex))

```
